What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-11 Manuscript/MS- What is LDD.tex
Edited Intro.

>>>>

An added difficulty to bridge ecological processes of dispersal with their genetic consequences is the fact that dispersal per se does not necessarily imply realized gene flow \citep{Mallet:2001wx}. Yet in the genetics literature, the inescapable difficulty to robustly estimate $\sigma_x$, the the standard deviation of parent-offspring distances, as an estimate of realized gene flow distance, is analogous to the ecological scenario. Strongly leptokurtic distributions of dispersal distances would lead to severe underestimation of $\sigma_x$, e.g., in mark-recapture studies limited to local sites where the long tail of LDD events escapes detection beyond the edges of the study area \citep{Mallet:2001wx}. Thus, fat-tailed distributions of dispersal distances tend to homogenize distant populations, leading to stronger reductions in $F_{st}$ than expected from local records of dispersal events \citep{Rousset:1997bd}.
